---
title: ''
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(tidyverse)
library(DBI)
library(dbplyr)
library(keyring)
library(vroom)
library(rJava)
library(mailR)

#Store file path to faxing home directory, include trailing slash
#key_set("sti-fax-dir")
fax_dir <- key_get("sti-fax-dir")

#store sti staff emails for follow up
#key_set("sti_supervisor_email")
#key_set("sti_provider_followup_email")
#key_set("sti_pm_email")

#load list of providers that prefer email to fax
email_providers <- readxl::read_excel(paste0(fax_dir, "providers-needing-email-follow-up.xlsx")) %>%
  mutate(match_key = paste(inedss_name, city))

```

Import database of STI provider contact information

```{r pull_providers}

#Note:Provider info kept in Microsoft Access database

#set pieces of database connection and construct string for provider database
provider_db_connect_string <- paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};", "DBQ=", fax_dir, "_ProviderContactDatabaseForMissingSurveillanceInfo.accdb")

#connect to provider info database
provider_db_connection <- dbConnect(odbc::odbc(), .connection_string = provider_db_connect_string)

#connect to database table with provider info and pull into R
all_providers <- tbl(provider_db_connection, "OrgListCurrentSTD") %>%
  #select(`Organization Name`, City, Fax) %>%
  collect() %>%
  janitor::clean_names() %>%
  mutate(across(where(is.character), ~na_if(.,""))) %>%
  mutate(across(where(is.character), toupper)) %>%
  mutate(match_key = paste(organization_name, city)) 
  
providers <- all_providers %>%
  select(organization_name, city, fax, match_key) %>%
  distinct() %>%
  group_by(match_key) %>%  #remove when duplicate provider issue fixed
  arrange(fax) %>%
  slice(n = 1) %>%
  ungroup()

#add step to filter out fax numbers starting with a 1
providers <- providers %>%
  filter(!grepl("^1.*|^\\(1.*", fax))

#close database connection
dbDisconnect(provider_db_connection)

```

Import files generated from auto case closure script of STI cases that couldn't be closed

```{r import_exceptions}

#import exception files dated in the last week
all_files <- list.files(path = 'sti-exceptions', pattern = ".*sti-exceptions.csv", full.names = T)  #end of year files are not ingested

files_this_week <- cbind(file = all_files,
              date = map_chr(all_files, ~str_extract(., "\\d{4}-\\d{2}-\\d{2}"))) %>%
  as.data.frame() %>%
  mutate(date = as.Date(date)) %>%
  filter(date > Sys.Date() - 7) %>%
  pull(file)

exceptions <- vroom(files_this_week) %>%
  distinct() 

```

Link STI cases needing closure to provider contact information

```{r match_providers}

#match exceptions to provider information on organization name and city
#special rules for ACHN clinics to ID correct city
exception_plus_provider <- exceptions %>%
  mutate(across(contains("Ordering"), toupper)) %>%
  separate(DiagnosisOrderingFacility, into = c("diagnosis_ordering_facility", "diagnosis_ordering_city", "diagnosis_ordering_phone"), sep = "; ") %>%
  mutate(matching_provider = ifelse(is.na(diagnosis_ordering_facility), OrderingFacilityName, diagnosis_ordering_facility),
         diagnosis_ordering_city = str_remove(diagnosis_ordering_city, ", .*"),
         diagnosis_ordering_phone = str_remove(diagnosis_ordering_phone, " "),
         ordering_city = case_when(
           #grepl(", [A-Z]{2} ", OrderingFacilityAddress) ~ sub("(^.*, )(.*)(, [A-Z]{2}.*$)", "\\2", OrderingFacilityAddress),
           grepl(", IL ", OrderingFacilityAddress) ~ sub("(^.*, )(.*)(, IL.*$)", "\\2", OrderingFacilityAddress),
           grepl("MORTON EAST ADOLESCENT", OrderingFacilityAddress) ~ "CICERO",
           OrderingFacilityName == "AMBULATORY COMMUNITY HEALTH NETWORK" ~ gsub("ACHN - | CLINIC.*$| HEALTH.*$| AMBULATORY.*$| MEDICAL.*$", "",OrderingFacilityAddress)),
         inedss_provider_city = trimws(ifelse(is.na(diagnosis_ordering_city), ordering_city, diagnosis_ordering_city))) %>%
  mutate(match_key = paste(matching_provider, inedss_provider_city)) %>%
  left_join(providers, by = "match_key") %>%
  #left_join(providers, by = c("matching_provider" = "organization_name", "inedss_provider_city" = "city")) %>%
  mutate(needs_email_followup = match_key %in% email_providers$match_key)  

#check for new variations of email provider facility names
exception_plus_provider %>% filter(grepl("ADVOCATE .* HOSPITAL|ADVOCATE .* MEDICAL CENTER|WESTLAKE URGENT",matching_provider)) %>% select(matching_provider, inedss_provider_city) %>% distinct() %>% View()

```

Remove cases that need manual follow up from STI staff and send to STI supervisor

```{r manual_follow_up}

#filter out cases requiring manual follow-up by STI Staff
#labs, out of state/missing provider city, or non-standard treatment used
manual_followup_cases <- exception_plus_provider %>%
  filter(grepl("LAB", matching_provider) | 
           grepl("non-standard treatment|inadequate treatment|case already exists for this person", Reason, ignore.case = T) | 
           is.na(inedss_provider_city)) %>%
    #select(Facility = matching_provider, StateCaseNumber:DiagnosisOrderingProvider, OrderingFacilityName:OrderingProviderPhone) %>%
  select(StateCaseNumber:Reason, Facility = matching_provider) %>%
  arrange(Facility) %>%
  filter(!grepl("\\d", Name))

#write file for follow up and email to STI supervisor
write_csv(manual_followup_cases, file = paste0(fax_dir, "Manual Follow Up/", Sys.Date(), "_sti-cases-needing-manual-follow-up.csv"))

if(file.exists(paste0(fax_dir, "Manual Follow Up/", Sys.Date(), "_sti-cases-needing-manual-follow-up.csv"))){

  send.mail(from = key_get("cch_auto_email"),
            to = c(key_get("sti_supervisor_email"), key_get("sti_provider_followup_email")),
            cc = key_get("smtp_user"),
            subject = "SECURELOCK: STI Cases Requiring Manual Follow Up",
            body = "The attached list of cases requires manual follow up from STI staff in order to close.",
            html = TRUE,
            smtp = list(host.name = key_get("smtp_host"), 
                        user.name = key_get("smtp_user"),
                        passwd = key_get("Office365"), tls = TRUE),
            attach.files = paste0(fax_dir, "Manual Follow Up/", Sys.Date(), "_sti-cases-needing-manual-follow-up.csv"),
            authenticate = TRUE,
            send = TRUE) 
  
}



```

Identify providers from the current case list that are missing from the provider database (or are in the provider database but are missing a fax number)

```{r missing_fax}

#generate lists of cases needing provider fax follow up
no_fax <- filter(exception_plus_provider, is.na(fax) & 
                   match_key %in% providers$match_key & 
                   !StateCaseNumber %in% manual_followup_cases$StateCaseNumber &
                   needs_email_followup == F)  #in provider DB but no fax
no_provider_record <- filter(exception_plus_provider, is.na(fax) & 
                               !match_key %in% providers$match_key &
                               !StateCaseNumber %in% manual_followup_cases$StateCaseNumber &
                               needs_email_followup == F) #doesn't exist in provider DB

#format file for providers who are in DB but missing fax
no_fax_clean <- all_providers %>%
  filter(match_key %in% no_fax$match_key & is.na(fax)) %>%
  select(organization_name:county) %>%
  distinct() %>%
  mutate(zip = as.integer(zip)) %>%
  arrange(organization_name) %>%
  janitor::clean_names(case = "title")

#write file for history
write_csv(no_fax_clean, file = paste0(fax_dir, "Provider Follow Up/", Sys.Date(), "_providers-with-missing-fax.csv"))

#set pieces of database connection and construct string for data entry database
addfax_db_connect_string <- paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};", "DBQ=", fax_dir, "AddProviderFax.accdb")

#connect to data entry database
addfax_db_connection <- dbConnect(odbc::odbc(), .connection_string = addfax_db_connect_string)

#pull in database of providers with no fax
db_no_fax <- tbl(addfax_db_connection, "Temp2") %>%
  collect() %>%
  mutate(Fax = NA,
         `Address Line 2` = ifelse(`Address Line 2` == "NA", NA, `Address Line 2`))

#append current no fax records to db table and de-duplicate
db_no_fax_append <- db_no_fax %>%
  bind_rows(no_fax_clean) %>%
  distinct()
  #distinct(`Organization Name`, City)

#overwrite table in database with new data
dbWriteTable(addfax_db_connection, "Temp2", db_no_fax_append, overwrite = T, batch_rows = 1)

#format file for providers who are not in DB
no_provider_record_clean <- no_provider_record %>%
  select(contains("ordering"), matching_provider, inedss_provider_city) %>%
  distinct() %>%
  mutate(organization_name = matching_provider,
         diagnosis_ordering_facility = ifelse(is.na(diagnosis_ordering_facility), "UNKNOWN", diagnosis_ordering_facility),
         provider = ifelse(matching_provider == diagnosis_ordering_facility, DiagnosisOrderingProvider, OrderingProviderName),
         address = ifelse(matching_provider == diagnosis_ordering_facility, diagnosis_ordering_city, OrderingFacilityAddress),
         phone_1 = ifelse(matching_provider == diagnosis_ordering_facility, diagnosis_ordering_phone, OrderingFacilityPhone),
         phone_2 = ifelse(matching_provider == diagnosis_ordering_facility, OrderingFacilityPhone, OrderingProviderPhone),
         phone_3 = ifelse(matching_provider == diagnosis_ordering_facility, OrderingProviderPhone, NA)) %>%
  select(organization_name, inedss_provider_city, provider:phone_3) %>%
  drop_na(organization_name, inedss_provider_city) %>%
  group_by(organization_name, inedss_provider_city) %>%
  summarise(provider_list = paste(unique(na.omit(provider)), collapse = "; "),
         address = address[which.max(nchar(address))],
         phone_list = paste(unique(na.omit(c(phone_1, phone_2, phone_3))), collapse = "; ")
         ) %>%
  ungroup() %>%
  rename(city = inedss_provider_city) %>%
  arrange(organization_name) %>%
  janitor::clean_names(case = "title")

#write files for history
write_csv(no_provider_record_clean, file = paste0(fax_dir, "Provider Follow Up/", Sys.Date(), "_providers-with-no-database-record.csv"))

#pull in database of providers with no fax
db_no_provider_record <- tbl(addfax_db_connection, "NOPROVIDER") %>%
  collect()

#append current no fax records to db table and de-duplicate
db_no_provider_record_append <- db_no_provider_record %>%
  bind_rows(no_provider_record_clean) %>%
  #distinct() %>%
  group_by(`Organization Name`, City) %>%  #prevent duplicates from being added to DB, take ones with most complete info
  arrange(Address, `Phone List`, `Provider List`) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(`Provider List` = strtrim(`Provider List`, 254))

#overwrite table in database with new data
dbWriteTable(addfax_db_connection, "NOPROVIDER", db_no_provider_record_append, overwrite = T, batch_rows = 1)

#close database connection
dbDisconnect(addfax_db_connection)

#send files for provider follow up to STI staff
if(file.exists(paste0(fax_dir, "Provider Follow Up/", Sys.Date(), "_providers-with-no-database-record.csv"))){

  send.mail(from = key_get("cch_auto_email"),
            to = key_get("sti_provider_followup_email"),
            cc = c(key_get("sti_supervisor_email"), key_get("smtp_user"), key_get("sti_pm_email")),
            subject = "New STI Providers Need Fax Follow Up",
            body = "Hello, new providers with missing fax numbers have been added to the STI AddFax database. Please visit the database and enter missing fax numbers for any providers in Form 1 and Form 2. Thank you!",
            html = TRUE,
            smtp = list(host.name = key_get("smtp_host"), 
                        user.name = key_get("smtp_user"),
                        passwd = key_get("Office365"), tls = TRUE),
            authenticate = TRUE,
            send = TRUE) 
  
}

```

Generate follow up faxes and emails to providers with known follow up information
 
```{r auto_follow_up}

#Import current follow-up history
fax_history <- read_csv("fax-history.csv", col_types = c("cci"))

#Run code below if faxes were generated but not sent previous week (re-adjust counter back by one)
# fax_history$fax_counter <- fax_history$fax_counter - 1
# fax_history <- filter(fax_history, fax_counter != 0)

#Create list of maxed out faxes/emails
maxed_out <- fax_history %>% filter(fax_counter >= 4) %>% pull(state_case_number)

#prepare list for follow-up
#remove manual cases, maxed out cases, clean provider name and clarify exceptions for provider audience
follow_up_cases <- exception_plus_provider %>%
  filter(!StateCaseNumber %in% manual_followup_cases$StateCaseNumber) %>%
  filter(!is.na(fax) | needs_email_followup) %>%
  filter(!StateCaseNumber %in% maxed_out) %>%
  mutate(diagnosis_provider_clean = sub(";.*", "", DiagnosisOrderingProvider),
         provider_clean = str_to_title(ifelse(is.na(diagnosis_provider_clean), OrderingProviderName, diagnosis_provider_clean))) %>%
  mutate(clean_reason = Reason,
         clean_reason = gsub("County must be specified. State is required. The patient's address must be validated before the case can be closed.|City is required for Illinois address, 'unknown' will be acceptable.|If State is not 'Illinois', County must be 'Out of State'. ", "Address is missing or invalid.", clean_reason),
         clean_reason = gsub("is required.|is blank.|is entered as Unknown.|must be specified.", "is missing.", clean_reason),
         clean_reason = gsub("If start date is not blank, an adequate treatment is required.", "Treatment is missing.", clean_reason),
         clean_reason = gsub("DOB and Current age cannot be blank.", "Date of birth is missing.", clean_reason),
         clean_reason = ifelse(grepl("Sites of Infection/Complications", Reason), "Name and/or address is missing or invalid.", clean_reason),
         clean_reason = ifelse(grepl("Sites of Infection/Complications", Reason) & grepl("Treatment is required.", Reason), paste(clean_reason, "Treatment is missing."), clean_reason)) %>%
  mutate(SpecimenCollectionDate = lubridate::mdy(SpecimenCollectionDate))

#separate cases for faxing
matched_fax_all <- follow_up_cases %>%
  filter(needs_email_followup == F) 
matched_fax <- split(matched_fax_all, matched_fax_all$match_key)

#Create directory to save faxes
dir.create(paste0(fax_dir,"Faxes/", Sys.Date()))

#Loop through list and write fax cover sheets
for (i in 1:length(matched_fax)) {
  
  #Extract provider data
  provider_data <- list(matched_fax[[i]])
  
  #Save provider name, file name, and fax num
  provider_name <- str_squish(gsub("[[:punct:]]", "", names(matched_fax)[i]))
  fax_file_name <- paste0(fax_dir,"Faxes/", Sys.Date(), "/", provider_name)
  fax_num <- gsub("[[:punct:]]", "", unique(provider_data[[1]]$fax)) 
  
  #Generate provider fax and save in directory
  rmarkdown::render(input = "provider-fax-template.Rmd",
                    output_file = fax_file_name,
                    params = list(data = provider_data))
  
  # #Pause for stability
  # Sys.sleep(2)
  # 
  # #Send fax to provider via e-fax system
  #   if (file.exists(paste0(fax_file_name, ".docx"))) {
  #   
  #       send.mail(from = key_get("cch_auto_email"),
  #           to = paste0("91", fax_num, "@fax.cookcountyhhs.org"),
  #           subject = "SECURELOCK: This is an official communication from the Cook County Department of Public Health. Please enclosed cover sheet.",
  #           body = " ",
  #           html = TRUE,
  #           smtp = list(host.name = key_get("smtp_host"), 
  #                       user.name = key_get("smtp_user"),
  #                       passwd = key_get("Office365"), tls = TRUE),
  #           attach.files = paste0(fax_file_name, ".docx"),
  #           authenticate = TRUE,
  #           send = TRUE) 
  #   
  #   }
  # 
  # #Pause for stability
  # Sys.sleep(3)
  
}

#separate cases for email 
matched_email_all <- follow_up_cases %>%
  filter(needs_email_followup) %>%
  left_join(email_providers, by = c("match_key")) 
matched_email <- split(matched_email_all, matched_email_all$system)

#Create directory to save emails
dir.create(paste0(fax_dir,"Emails/", Sys.Date()))

#Loop through list and write memos for emails
for (i in 1:length(matched_email)) {
  
  provider_data <- list(matched_email[[i]])
  provider_name <- str_squish(gsub("[[:punct:]]", "", names(matched_email)[i]))
  rmarkdown::render(input = "provider-fax-template-email.Rmd",
                    output_file = paste0(fax_dir,"Emails/", Sys.Date(), "/", provider_name),
                    params = list(data = provider_data))
  
}

#Loop through list and send email memos
for (i in 1:length(matched_email)) {
  
  provider_name <- str_squish(gsub("[[:punct:]]", "", names(matched_email)[i]))
  file_name <- paste0(fax_dir,"Emails/", Sys.Date(), "/", provider_name, ".docx")
  email <- matched_email[[i]]$email %>% unique()
  
  if (file.exists(file_name)) {
    
        send.mail(from = key_get("cch_auto_email"),
            to = email,
            cc = key_get("smtp_user"),
            subject = "SECURELOCK: STI Cases Reported to CCDPH Require Follow Up",
            body = "The attached file contains information on patients missing required information in I-NEDSS. Please update the case record in I-NEDSS or fax a complete STI morbidity report form for each patient. Thank you!<br><br> <i>Note: Please do not reply directly to this email. This email address is not monitored.</i>",
            html = TRUE,
            smtp = list(host.name = key_get("smtp_host"), 
                        user.name = key_get("smtp_user"),
                        passwd = key_get("Office365"), tls = TRUE),
            attach.files = file_name,
            authenticate = TRUE,
            send = TRUE) 
    
  }

}


#For cases being faxed or emailed for the first time, add to fax history
new_cases <- follow_up_cases %>%
  filter(!StateCaseNumber %in% fax_history$state_case_number) %>%
  select(state_case_number = StateCaseNumber, event_date = EventDate) %>%
  mutate(event_date = as.character(event_date),
         fax_counter = 0)  #counter will iterate to 1 below

fax_history <- bind_rows(fax_history, new_cases)

#Increment fax counter for cases sent
fax_history <- fax_history %>% 
  mutate(fax_counter = ifelse(state_case_number %in% unique(c(matched_fax_all$StateCaseNumber, matched_email_all$StateCaseNumber)), fax_counter + 1, fax_counter))

#Re-save fax history
write_csv(fax_history, "fax-history.csv")


```
 

 
 
